% $Id: appendix-simulation-details.tex 435 2018-12-17 22:53:31Z mspannow $
\chapter{Details of Monte Carlo simulations}\label{chap:app-simulation-details}

In this appendix, we provide the details of the parton-shower Monte Carlo
simulations presented throughout this book.

For all the results shown in
Chapters~\ref{calculations-substructure-mass},
\ref{sec:calc-shapes-qg} and \ref{sec:curiosities}, we have used the
Pythia~8 generator~\cite{Sjostrand:2014zea,Sjostrand:2007gs} (version
8.230) with the Monash 2013 tune~\cite{Skands:2014pea}.
%
The analytic results are always compared to Monte Carlo results at
parton level, where both hadronisation and the Underlying Event have
been switched off.
%
The ``hadron level'' corresponds to switching on hadronisation but
keeping multi-parton interactions off, while the ``hadron+UE'' level
includes both hadronisation and the Underlying Event.
%
In the last two cases, $B$-hadrons have been kept stable for
simplicity.\footnote{Except for the groomed jet mass study in
  Sec.~\ref{sec:calc-groomed-mass-mc} where $B$-hadron decays are
  enabled.}
%
For the samples labelled as ``quark jets'', we have used Pythia's
dijet hard processes, keeping only the $qq\to qq$ matrix
elements. Similarly the ``gluon jet'' samples keep only the $gg\to gg$.

For all studies, jet reconstruction and manipulations are performed
using FastJet~\cite{Cacciari:2011ma,Cacciari:2005hq}
(version~3.3). Our studies include all the jets above the specified
$p_t$ cut and with $|y|<4$.
%
Substructure tools which are not natively included in FastJet are
available from {\tt {fastjet-contrib}}.

In the case of the discrimination between boosted W jets and QCD
jets in Chapter~\ref{chap:calc-two-prongs}, we have used the same
samples as those used in the initial Les-Houches 2017 Physics at TeV
colliders workshop.
%
These use essentially the same generator settings as above, but now
only up to the two hardest jets with $|y|<2.5$ are kept.


%% GS helper for auctex
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "notes"
%%% End:

%  LocalWords:  Monash UE Pythia's qq gg natively Houches
